---
title: 
author: 
date: 
output:
  html_document:
    highlight: textmate
    theme: readable
    toc: yes
    toc_depth: 1
   # toc_float: yes
runtime: shiny
---

```{r libs, include=FALSE, echo=FALSE}

library(utils)
library(stats)
library(utils)
library(datasets)
library(graphics)
library(shiny)
library(grDevices)
library(methods)
library(leaflet)
library(dplyr)
library(shinycssloaders)
library(rgdal)
library(plotly)
library(htmltools)
library(DT)
library(shinyjs)
library(shinythemes)
library(rsconnect)
library(tidyr)
library(tidyverse)



data1<- read.csv(file = 'ADFGDataSummary.csv')   #aerial survey and escapement dataset
data2<- read.csv(file = 'ADFG_ASL.csv')         # ASL data set
data <- left_join(data1, data2[,3:10], by = "Location", all= FALSE)%>% #merging dataset
          filter_at(vars(First_Year,Last_Year),all_vars(!is.na(.)))   # only keeping ASL data that has accompanying survey data


```

## Chinook Salmon Data for the Arctic-Yukon-Kuskokwim Region {.tabset}

### Survey Data
Query data based on 1) Management Area, 2) Survey type, 3) number of years of return observations 4) average return size and 5) number of years of ASL observations. Once data has been queried, select "View Selection on Map" and the datasets will be plotted. Click on points to see more information regarding the data for that location.

Detailed graphs of the overlap between ASL and return counts from escapement surveys can be viewed in the 'Dataset Overlap' tab.  

**Map colors** correspond to survey type, either 'escpement' (red) or 'aerial survey' (navy)

**Point size** corresponds to the number of years of data observations

```{r, echo=FALSE}
shinyApp(
ui = fluidPage(theme = shinytheme("flatly"),
  sidebarLayout(
    sidebarPanel(  
      h3("Query Data"),
      br(),
      
      radioButtons(inputId = "Management_Area", #radio button for whether there is ASL data
                   label= "Management Area:",
                   c("Yukon (US)" = "Yukon (US)",
                     "Yukon (CA)" = "Yukon (CA)",
                     "Kuskokwim" = "Kuskokwim",
                     "Norton Sound" = "Norton Sound",
                     "Kotzebue" = "Kotzebue",
                     "All Areas" = "All"),
                   selected="All"),
      
  radioButtons(inputId = "Project_Type", #radio button for whether there is ASL data
               label= "Survey Type:",
               c("Escapement Counts" = "Escapement Counts",
                 "Aerial Survey" = "Aerial Survey",
                 "All Data" = "All"),
               selected="All"),
 
 
   sliderInput("Number_of_Years", #slider for the minimum number of escapement observations
              "Minimum Number of Years of Survey Observations:",
              min = 0,
              max = 60,
              step=1,
              value = 1),
  
  sliderInput("Avg_Count", #radio button for the minimum escapement size
              "Minimum Average Return:",
              min = 0,
              max = 5000,
              step= 20,
              value = 20),
  
  sliderInput("Min_ASL", #radio button for the minimum escapement size
              "Minimum Number of Years for ASL Data:",
              min = 0,
              max = 60,
              step= 1,
              value = 0),
  
  actionButton(
    "select_all_rows_button",
    "View Selection on Map"
  ),
  
  actionButton(
    "clear_rows_button",
    "Clear Map Selection"
    
  )

  
    ),
  
  mainPanel(
    h4("Map of Data"),
        leafletOutput(
          "my_leaflet"
        ),
    
 
    h4("Data Inventory"),
        DTOutput(
          "my_datatable"
        )
      )
    )
  )
,

 server = function(session, input, output) {
#Creating a reactive dataset that can be filtered by the slider and the radio buttons from the ui  
  filtered_data <- reactive({ 
   data <-  data %>%
      filter(Number_of_Years >= input$Number_of_Years & 
               Avg_Count >= input$Avg_Count &
               Number_of_Years_ASL >= input$Min_ASL)  

   
   #assigning the correct filtering for management area 
   if(input$Management_Area == "Yukon (US)"){
     data <- data %>% filter(Management_Area == "Yukon")
   }else{
     if(input$Management_Area == "Yukon (CA)"){
       data<-  data %>% filter(Management_Area == "Yukon - Canada")
     }else{
       if(input$Management_Area == "Kuskokwim"){
         data<-  data %>% filter(Management_Area == "Kuskokwim")
       }else{
         if(input$Management_Area == "Kotzebue"){
           data<-  data %>% filter(Management_Area == "Kotzebue")
         }else{
           if(input$Management_Area == "Norton Sound"){
             data<-  data %>% filter(Management_Area == "Norton Sound/Port Clarence")
             }else{
               data
             }
           }
         }
       }
     }
   
    #assigning the correct filtering for survey type  
       if(input$Project_Type == "Escapement Counts"){
          data <- data %>% filter(Project_Type == "Escapement")
        }else{
          if(input$Project_Type == "Aerial Survey"){
           data<-  data %>% filter(Project_Type == "Aerial Survey")
          }else{
            data
          }
        }
})
  

  #creating the output data table that will be filtered by the slider and the buttons  
  output$my_datatable <- renderDT({
    
    filtered_data() %>% 
       datatable( rownames = FALSE,  class = "display", fillContainer = T, 
                  options = list( scrollX = TRUE, 
                                 paging = FALSE))
  })
  
  pal <- colorFactor(c("navy", "red"), domain = c("Escapement", "Aerial Survey"))  
  # base map that we will add points to with leafletProxy(), using a proxy means the map does not need to be redrawn
  output$my_leaflet <- renderLeaflet({
    
    leaflet() %>% 
      addProviderTiles(
        provider = providers$CartoDB.Positron,
        options = providerTileOptions(
          noWrap = FALSE
        )
      ) %>% 
      setView(
        lat = 62.8883491, #the map can zoom, but this is the default area it is centered on
        lng = -160.5594136,
        zoom = 4
      )
    
  })
  
  #this initiates and event that allows selected rows in the data table to pop up on the map, using the "clear all" 
  #and 'select all" action button initiated in the ui
  
  observeEvent(input$my_datatable_rows_selected, {
    
    selected_lats <- eventReactive(input$my_datatable_rows_selected, {
      as.list(filtered_data()$Latitude[c(unique(input$my_datatable_rows_selected))])
    })
    
    selected_longs <- eventReactive(input$my_datatable_rows_selected, {
      as.list(filtered_data()$Longitude[c(unique(input$my_datatable_rows_selected))])
    })
    
    selected_location <- eventReactive(input$my_datatable_rows_selected, {
      as.list(filtered_data()$Location[c(unique(input$my_datatable_rows_selected))])
    })
    
    selected_management <- eventReactive(input$my_datatable_rows_selected, {
      as.list(filtered_data()$Management_Area[c(unique(input$my_datatable_rows_selected))])
    })
    
    selected_type <- eventReactive(input$my_datatable_rows_selected, {
      as.list(filtered_data()$Project_Type[c(unique(input$my_datatable_rows_selected))])
    })
    
    selected_avg <- eventReactive(input$my_datatable_rows_selected, {
      as.list(filtered_data()$Avg_Count[c(unique(input$my_datatable_rows_selected))])
    })
    
    selected_nyears <- eventReactive(input$my_datatable_rows_selected, {
      as.list(filtered_data()$Number_of_Years[c(unique(input$my_datatable_rows_selected))])
    })
    
    
    # this is the data that will be passed to the leaflet in the addCircleMarkers argument,
    # as well as the popups when the points are hovered over
    map_df <- reactive({
      tibble(lat = unlist(selected_lats()),
             lng = unlist(selected_longs()),
             location = unlist(selected_location()),
             management = unlist(selected_management()),
             nyears = unlist(selected_nyears()),
             average = unlist(selected_avg()),
             type = unlist(selected_type()))
    })
    leafletProxy("my_leaflet", session) %>% 
      clearMarkers() %>% 
      addCircleMarkers(
        data = map_df(),
        lng = ~lng,
        lat = ~lat,
        stroke = TRUE,
        color = ~pal(type),
        radius = 1,
        weight = ~nyears/2,
        fillOpacity = 0.4,
        popup = paste0("Name: ", map_df()$location, "<br>",
                       "Region: ", map_df()$management, "<br>",
                       "Data Type: ", map_df()$type, "<br>",
                       "Average Return: ", map_df()$average, "<br>",
                       "# Years of Escapement Data: ", map_df()$nyears)
                       
      )
    
  })
  
  # create a proxy to modify datatable without recreating it completely
  DT_proxy <- dataTableProxy("my_datatable")
  
  # clear row selections when clear_rows_button is clicked
  observeEvent(input$clear_rows_button, {
    selectRows(DT_proxy, NULL)
  })
  
  # clear markers from leaflet when clear_rows_button is clicked
  observeEvent(input$clear_rows_button, {
    clearMarkers(leafletProxy("my_leaflet", session))
  })
  
  # select all rows when select_all_rows_button is clicked
  observeEvent(input$select_all_rows_button, {
    selectRows(DT_proxy, input$my_datatable_rows_all)
  })
  
}
,

  options = list(height = 500)
)
```

**Note**: not all ASL data is included/assigned to a location in this dataset, only escapment ASL and ancillary ASL that could be assigned to a specific river was included. Aditional test fishing and harvest ASL is also available and is described in the "Detailed ASL" tab.

### Dataset Overlap

Temporal overlap in between escapement counts, aerial surveys, and ASL data for locations with escapement count. Age data includes both escapement ASL and ancillary age data. Weir, tower, sonar, and aerial survey data are plotted separately to identify overlaps and gear changes

``````{r, echo=FALSE}
data.plot <- read.csv(file = 'DataSumm_EscHarAge.csv')

shinyApp(

  ui = fluidPage(
    selectInput("Region", "Region:",
                choices = c('Yukon (CA)',
                            'Yukon (US)',
                            'Kuskokwim',
                            'Norton Sound')),
    plotOutput("detailedPlot")
  ),

  server = function(input, output) {
    
    filtered_data <- reactive({ 
      data <-  data.plot %>%
      filter(Region == input$Region) %>% 
      gather(key= "DataType",value="Escapement",Age, Aerial.Survey, Escapement..weir., Escapement..tower., Escapement..sonar.)
       
    })
    
    output$detailedPlot = renderPlot({
ggplot(data = filtered_data(), aes(x = Year,  y=DataType, size = Escapement, col=DataType)) + geom_point(alpha=0.7)+
facet_wrap(~Location)+
scale_size(range = c(2, 2), limits = c(0.5, 1.5))

    })
  },

  options = list(height = 500)
)
```
**Note**: Aerial survey data is inclusive of all years data is available from ADFG. Some aerial survey data displayed may be poorly rated, contain incomplete spatial coverage, or the spatial extent may vary between surveys. This shows what is available but not necessarily what will ultimately be "usable".

Escapement data years that were marked as 'poor' in the ADFG website (i.e. more than 40% of run was missed) were omitted from this plot. Displayed escapement date should approximately represent what is 'usable'.

ASL data includes both escapement ASL and ancillary ASL for a given escapement location.


### Detailed ASL
We show a scatter plot in this section.

```{r, echo=FALSE}
data.ASL <- read.csv(file = 'ADFG_ASL.csv')

shinyApp(

  ui = fluidPage(theme = shinytheme("flatly"),
  sidebarLayout(
    sidebarPanel(  
      h3("Query Data"),
      br(),
      
        sliderInput("Avg_Sampled_ASL", #slider for minimum number of individuals sampled
              "Minimum Individuals Sampled:",
              min = 0,
              max = 1000,
              step= 20,
              value = 0),
  
  sliderInput("Number_of_Years_ASL", #slider for minimum number of years
              "Minimum Number of Years for ASL Data:",
              min = 0,
              max = 60,
              step= 1,
              value = 0),
  
     radioButtons(inputId = "Management_Area", #radio button for whether there is ASL data
                   label= "Management Area:",
                   c("Yukon (US)" = "Yukon (US)",
                     "Yukon (CA)" = "Yukon (CA)",
                     "Kuskokwim" = "Kuskokwim",
                     "Norton Sound" = "Norton Sound",
                     "Kotzebue" = "Kotzebue",
                     "All Areas" = "All"),
                   selected="All")),
     

  mainPanel(    
     DTOutput(
          "my_datatable"
        )
  )
  )
  ),

   server = function(input, output){
    
    filtered_data <- reactive({ 

 data.ASL <-  data.ASL %>%
      filter(Number_of_Years_ASL >= input$Number_of_Years_ASL & 
               Avg_Sampled_ASL >= input$Avg_Sampled_ASL) 
      
   #assigning the correct filtering for management area 
   if(input$Management_Area == "Yukon (US)"){
     data.ASL<- data.ASL %>% filter(Management_Area == "Yukon")
   }else{
     if(input$Management_Area == "Yukon (CA)"){
       data.ASL<-  data.ASL %>% filter(Management_Area == "Yukon - Canada")
     }else{
       if(input$Management_Area == "Kuskokwim"){
         data.ASL<-  data.ASL %>% filter(Management_Area == "Kuskokwim")
       }else{
         if(input$Management_Area == "Kotzebue"){
           data.ASL<-  data.ASL %>% filter(Management_Area == "Kotzebue")
         }else{
           if(input$Management_Area == "Norton Sound"){
             data.ASL<-  data.ASL %>% filter(Management_Area == "Norton Sound/Port Clarence")
             }else{
               data.ASL
             }
           }
         }
       }
     }
    
    })
    
     output$my_datatable <- renderDT({
    
    filtered_data() %>% 
       datatable( rownames = FALSE,  class = "display", fillContainer = T, 
                  options = list( scrollX = TRUE, 
                                 paging = FALSE))
  })
})
```

### Detailed Harvest

Harvest data for commercial and subsistence fisheries

``````{r, echo=FALSE}
data.har <- read.csv(file = 'ADFG_Harvest.csv')

shinyApp(

  ui = fluidPage(theme = shinytheme("flatly"),
  sidebarLayout(
    sidebarPanel(  
      h3("Query Data"),
      br(),
     radioButtons(inputId = "Region", #radio button for whether there is ASL data
                   label= "Region:",
                   c("Yukon (US)" = "Yukon (US)",
                     "Yukon (CA)" = "Yukon (CA)",
                     "Kuskokwim" = "Kuskokwim",
                     "Norton Sound" = "Norton Sound",
                     "Kotzebue" = "Kotzebue",
                     "All Areas" = "All Areas"),
                   selected="All Areas"),
     
      radioButtons(inputId = "HarvestType", #radio button for whether there is ASL data
                   label= "Harvest Type:",
                   c("Commercial Harvest (Pre-1985)" = "Commercial Harvest (Pre-1985)",
                     "Commercial Harvest (Post-1985)" = "Commercial Harvest (Post-1985)",
                     "Subsistence" = "Subsistence",
                     "All Types" = "All Types"),
                   selected="All Types")),
  mainPanel(    
     DTOutput(
          "my_datatable"
        )
  )
  )
  ),

   server = function(input, output){
    
    filtered_data <- reactive({ 

    #assigning the correct filtering for management area 
    if(input$HarvestType == "Commercial Harvest (Post-1985)"){
      data.har <- data.har %>% filter(Project_Type == "Commercial Harvest (Post-1985)")
    }else{
      if(input$HarvestType == "Commercial Harvest (Pre-1985)"){
        data.har<-  data.har %>% filter(Project_Type == "Commercial Harvest (Pre-1985)")
      }else{
        if(input$HarvestType == "Subsistence"){
          data.har<-  data.har %>% filter(Project_Type == "Subsistence")
            }else{
              data.har
            }
          }
        }
      
          if(input$Region == "Yukon (US)"){
      data.har <- data.har %>% filter(Region == "Yukon (US)")
    }else{
      if(input$Region == "Yukon (CA)"){
        data.har<-  data.har %>% filter(Region == "Yukon - Canada")
      }else{
        if(input$Region == "Kuskokwim"){
          data.har<-  data.har %>% filter(Region == "Kuskokwim")
        }else{
          if(input$Region == "Kotzebue"){
            data.har<-  data.har %>% filter(Region == "Kotzebue")
          }else{
            if(input$Region == "Norton Sound"){
              data.har<-  data.har %>% filter(Region == "Norton Sound")
            }else{
              data.har
            }
          }
        }
      }
    }
      
    
    })
    
     output$my_datatable <- renderDT({
    
    filtered_data() %>% 
       datatable( rownames = FALSE,  class = "display", fillContainer = T, 
                  options = list( scrollX = TRUE, 
                                 paging = FALSE))
  })
})
    
    

```

